Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-03 paper/ms.tex
correlation plots added and changes in the paper in the correlation section added

We limit the occupation fraction to
be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
and the uncertainty in the dust correction used to infer the escape fraction. 
Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
With this additional constraint between $35$ to $40$ models are
consistent with observations, this represents a factor of $\sim 2$
reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
excluded and the best models are now clustered around a narrow region
in parameter space. The list for the model parameters is in the
Appendix in Table \ref{table:models_match}.

@@

We also present the ACF in the case of the full SSA22
region which has been homogeneously observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions.

@@

We also present the results for the angular correlation function in
therms of the correlation lenght obtained by fitting the following
function
\begin{equation}
\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
\end{equation}

The results are shown in Figure in a $r_{0}-\gamma$ plane where the
average and standard deviation for each mock are shown in comparison
with the result derived from observations.

%We calculate the mean angular correlation function (ACF) only for the
%models that showed that all of the 15 mock surveys are consistent
%at the $P>0.05$ level with observations.

Figure \ref{figure:correlation_match} (match) and Figure
\ref{figure:correlation_random} (random) present such comparison.  The
error bars in these figures represent the standard deviation of the
ACF over all the sub-fields.  In general, we observe that the standard
deviation of the computed ACF in the subfields increases with
$M_{min}$ following the same trend as in Figure
\ref{figure:laes_dist}, as a direct consequence of cosmic variance.

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_%selected_models.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_s%elected_models.pdf}
%\end{center} f
%\caption{ mean ACFs   and their correponding standard deviation (error
%  bars)  of some selected models in different mass ranges over the 7
%  subfields  f the SSA22 field (left) and the entire 12 field sample
%  (rigth) using thematch
%  configuration. \label{figure:correlation_match} }  
%  \end{figure*}

@@

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.6& 11.7& 0.1\\
10.6& 10.8& 0.2\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
10.9& 12.0& 0.2\\
10.9& 12.1& 0.2\\
10.9& 12.2& 0.2\\
10.9& 12.3& 0.2\\
10.9& 12.4& 0.2\\
10.9& 12.5& 0.2\\
10.9& 12.6& 0.2\\
10.9& 12.7& 0.2\\
10.9& 12.8& 0.2\\
10.9& 12.9& 0.2\\
10.9& 13.0& 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{List of model parameters for the best models that have all
  mock surveys consistent with observations and an occupation
  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
    match} method to construct the mock surveys. \label{table:models_match}. }
\end{table}

>>>>

We limit the occupation fraction to
be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
and the uncertainty in the dust correction used to infer the escape fraction. 
Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
With this additional constraint between $35$ to $40$ models are
consistent with observations, this represents a factor of $\sim 2$
reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
excluded and the best models are now clustered around a narrow region
in parameter space. %The list for the model parameters is in the
%Appendix in Table \ref{table:models_match}.

@@

We also present the results for the mean angular correlation function in
therms of the angular correlation lenght obtained  by fitting to a power-law
function:

\begin{equation}
\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
\end{equation}

The fitting is done to both the mean ACF and the observational
ACF reported by \cite{Hayashino2004} .  The results are shown 
in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
plane where the average and standard deviation for each mock 
are shown in comparison with the result derived from observations. 
Error bars in these figures represents the standard deviation of the
ACF over all the sub-fields.

It can be seen in the left panel figure \ref{figure:correlation_parameters} that
The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
constrains on the parameters models. Only models with angular-correlation lenght within  
$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.

In order to identify the models that are consistent with observation we
plot if the right panel of figure \ref{figure:correlation_parameters} 
$\theta_{0}$ vs $M_{\rm min}$ and divide the plots into two sets: Those models
with $\log \frac{M_{\rm max}}{M_{\odot}}<12$ (blue dots) and those with 
$\log \frac{M_{\rm max}}{M_{\odot}}>12$ (green dots). The red rectangle includes
the parameter region wich is consistent with the observational constraint in $\theta_{0}$.
With this restriction we find that models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and
$\log \frac{M_{\rm min}}{M_{\odot}}>11.1$can be ruled out.

%In general, we observe that the standard
%deviation of the computed ACF in the subfields increases with
%$M_{min}$ following the same trend as in Figure
%\ref{figure:laes_dist}, as a direct consequence of cosmic variance.

Finally, we also present the ACF in the case of the full SSA22
region which has been homogeneously observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}
\end{center}
\caption{Left: The fitted parameters  ($\theta_{0}$ vs $\gamma$) of the 
mean ACF  assuming a powerlaw behavior. Each blue dot corresponds to a
match-model while the green dot represent the powerlaw fit of the observational
ACF reported by \cite{Hayashino2004}.  The error bars represents the dispersion
in each parameter over all the mock surveys for a given model and dispersion due
to the observational error for the measured ACF by \cite{Hayashino2004}. Rigth: 
$\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
(blue) and $M_{max}>12.0$ (green). The red rectangle includes the region within
models are consisted with the observational angular-correlation lenght
($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters} }  
\end{figure*}

@@

When we additional include the ACF constraint we find that only models with 
$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
are now consistent with observations.

Including all the observational constraints we find that only between $15$ to $20$ 
models reproduces observations. The list for the model parameters is in the
Appendix in Table \ref{table:models_match}.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.6& 11.7& 0.1\\
10.6& 10.8& 0.2\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
%10.9& 12.0& 0.2\\
%10.9& 12.1& 0.2\\
%10.9& 12.2& 0.2\\
%10.9& 12.3& 0.2\\
%10.9& 12.4& 0.2\\
%10.9& 12.5& 0.2\\
%10.9& 12.6& 0.2\\
%10.9& 12.7& 0.2\\
%10.9& 12.8& 0.2\\
%10.9& 12.9& 0.2\\
%10.9& 13.0& 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{List of model parameters for the best models that have all
  mock surveys consistent with observations and an occupation
  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
    match} method to construct the mock surveys. \label{table:models_match}. }
\end{table}
